OptiFit: a fast method for fitting amplicon sequences to existing OTUs

### 2021-08-10 paper/paper.Rmd
Start writing importance section...

**TODO.**
<!--
**"AND, BUT, THEREFORE" structure. start paragraph with question, end with why we should care. transitions to move the story along.**
Advancements in sequencing technology have allowed researchers to affordably generate millions of reads of microorganisms from diverse natural communities,
allowing us to characterize communities.
-->
\newpage

>>>>

**TODO.**
Advancements in DNA sequencing technology have allowed researchers to affordably
generate millions of reads from microorganisms in diverse natural communities.
allowing us to characterize communities.
\newpage
